---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Nunito:wght@300;400;700&display=swap');

body {
    font-family: 'Roboto', sans-serif;
    background: #50abe7;
    color: #ffffff;
    margin: 50px 30px;
    line-height: 1.6;
}

h2 {
    font-family: 'Nunito', sans-serif;
    color: #ffffff;
    font-weight: bold;
}

h1 {
    font-family: 'Nunito', sans-serif;
    color: #ffffff;
    font-weight: bold;
    border: 2px solid #ffffff;
    padding: 10px;
    background-color: #bae0f3;
    border-radius: 10px;
}

p {
    font-size: 1.2em;
    text-align: justify;
}

```

# Analyzing Student Laptop Usage and Activities

This analysis explores device usage, activities, and screen counts among University of Auckland students. The primary focus of the data collection was to understand the types of devices students use for academic and campus-related activities, such as whether they use MacBooks or Windows laptops. Additionally, the data aims to explore the various activities students engage in, including studying, browsing, or attending online lectures, and to evaluate the effectiveness of the newly installed monitors at key locations like the Kate Edger Information Commons. By understanding these patterns, we can assess whether the new monitors are being fully utilized for academic purposes and identify any device preferences that could enhance future resource planning at the university.

```{r}
# Load tidyverse package
library(tidyverse)

# Inputting the CSV file into rstudio
logged_data <- read_csv("https://raw.githubusercontent.com/CH3M1R1/stats220/refs/heads/main/STATS%20220%20-%20Project%202%20(Responses)%20-%20Form%20responses%201.csv")

# Renaming variables
latest_data <- logged_data %>%
  rename(
    Timestamp = 'Timestamp',
    Device_type = 'What type of laptop was the student using?',
    Activity = 'What were they doing',
    Screen_count = 'How many screens were they using?'
  )

# _DATA EXPLORATION_

# Counts how many total amount of screens 
total_screens <- sum(latest_data$Screen_count)

# Counts how many data was recorded
data_count <- nrow(latest_data)

# Average number of screens students used
average_screens <- mean(latest_data$Screen_count)

# _BAR CHARTS_

# Bar Chart 1 - Counting student device types
barchart_1 <- ggplot(latest_data, aes(x = Device_type, fill =  Device_type)) +
  geom_bar(stat = "count") +
  labs(
    title = "Student Laptop Types"
  )

# Bar Chart 2 - Student activities
barchart_2 <- ggplot(latest_data, aes(x = Activity, fill = Activity)) +
  geom_bar(stat = "count") +
  labs(
    title = "Student Activity"
  )

# These summary values and visualizations provide insights into student device usage and help assess the effectiveness of the new monitors installed at the University of Auckland.

```

# Bar Graphs

## Device Usage Among Students

```{r}
print(barchart_1)
```

This bar chart visualizes the distribution of different laptop types used by students at the University of Auckland. It highlights the most popular device choices, offering insights into the technological preferences of the student body. Understanding which devices are most commonly used can help the newer university students make informed decisions about which products would students prefer to use when studying.

In which seen in this graph, students prefer to buy apple products such as macbooks, this could be due to their light weight design and smooth fucntionality.

## Student Activity Breakdown
```{r}
print(barchart_2)
```

This chart displays the various activities students engage in while using their laptops. By categorizing the tasks into studying, browsing, watching online lectures, and other activities, this chart helps identify the most common behaviors on campus. This breakdown could be valuable for designing spaces that better support student needs, such as creating areas for collaborative work or quiet study spaces.

# Data Summary

## Total Screens Used by Students
The total number of screens recorded among University of Auckland students is `r total_screens`. This reflects the total number of screens in use across all student activities during the data collection period. Understanding this number is essential for evaluating the demand for additional screens and monitors in the campus environment, especially in high-traffic study areas.

## Total Data Entries Recorded
The total number of data entries collected for this analysis is `r data_count`

## Average Number of Screens Used
On average, University of Auckland students were using `r average_screens` screens during their activities. This metric is useful for assessing whether students are utilizing multiple screens for multitasking purposes or relying on single devices for their study needs. This number also provides insight into the adoption of multi-screen setups.
