---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
@import url('https://fonts.googleapis.com/css2?family=Nunito:wght@300;400;700&display=swap');

body {
    font-family: 'Roboto', sans-serif;
    background: #50abe7;
    color: #ffffff;
    margin: 50px 30px;
    line-height: 1.6;
}

h2 {
    font-family: 'Nunito', sans-serif;
    color: #ffffff;
    font-weight: bold;
}

h1 {
    font-family: 'Nunito', sans-serif;
    color: #ffffff;
    font-weight: bold;
    border: 2px solid #ffffff;
    padding: 10px;
    background-color: #bae0f3;
    border-radius: 10px;
}

p {
    font-size: 1.2em;
    text-align: justify;
}

```

# Analyzing Student Laptop Usage and Activities

This analysis explores device usage, activities, and screen counts among University of Auckland students to identify common study habits and device preferences. It provides insights into the types of devices students prefer and how they spend their time on campus. Additionally, this analysis helps determine whether the new monitors installed around the university are being effectively utilised.

```{r}
# Load tidyverse package
library(tidyverse)

# Inputting the CSV file into rstudio
logged_data <- read_csv("C:/Users/chemi/OneDrive/Desktop/Stats 220/STATS 220 - Project 2/STATS 220 - Project 2 (Responses) - Form responses 1.csv")

# Renaming variables
latest_data <- logged_data %>%
  rename(
    Timestamp = 'Timestamp',
    Device_type = 'What type of laptop was the student using?',
    Activity = 'What were they doing',
    Screen_count = 'How many screens were they using?'
  )

# _DATA EXPLORATION_

# Counts how many total amount of screens 
total_screens <- sum(latest_data$Screen_count)

# Counts how many data was recorded
data_count <- nrow(latest_data)

# Average number of screens students used
average_screens <- mean(latest_data$Screen_count)

# _BAR CHARTS_

# Bar Chart 1 - Counting student device types
barchart_1 <- ggplot(latest_data, aes(x = Device_type, fill =  Device_type)) +
  geom_bar(stat = "count") +
  labs(
    title = "Student Laptop Types"
  )

# Bar Chart 2 - Student activities
barchart_2 <- ggplot(latest_data, aes(x = Activity, fill = Activity)) +
  geom_bar(stat = "count") +
  labs(
    title = "Student Activity"
  )

```

# Bar Graphs

## Device Usage Among Students

```{r}
print(barchart_1)
```

This bar chart shows the distribution of different laptop types used by students at the University of Auckland. It highlights the most common device choices, giving insight into student preferences for academic work and campus activities.

## Student Activity Breakdown
```{r}
print(barchart_2)
```

This chart displays the various activities students engage in while using their laptops. It categorizes the most common tasks performed, such as studying, browsing, or watching online lectures, to help identify key student behaviors and priorities.

# Data Summary

## Total Screens Used by Students
The total number of screens recorded among University of Auckland students is `r total_screens`

## Total Data Entries Recorded
The total number of data entries collected for this analysis is `r data_count`

## Average Number of Screens Used
On average, University of Auckland students were using `r average_screens` screens during their activities
